---
title: "BLS Regional and sectoral unemployment analysis - TEST 2"
author: ''
date: ''
output:
  pdf_document: default
  html_document:
    fig_height: 4
    fig_width: 6
---
<!-- XXXXX -->
```{r include=FALSE}
library(DataComputing)
library(mosaic)
library(dplyr)
library(tidyr)
library(knitr)
library(printr)

setwd("C:\\Users\\M. Looter King Jr\\Desktop\\133 Desktop")
```
*Source file* 
```{r, results='asis', echo=FALSE}
includeSourceDocuments()
```
<!-- XXXXX -->

# Load downloaded data

1998 annual Census on Employment and Wages (CWE)
```{r, results='hide'}
a1998.csv <- "1998.annual.singlefile.csv"
a1998 <- a1998.csv %>% 
  read.file()
```

```{r, include = FALSE}
head(a1998)
```

Industry title translations
```{r}
indu.csv <- "industry_titles.csv"
indu <- indu.csv %>% 
  read.file()

head(indu)
```

Area title translations
```{r}
area.csv <- "area_titles.csv"
area <- area.csv %>% 
  read.file()

head(area)
```

# Joining 1998 CWE and translation tables

```{r}
a1998.j <- a1998 %>%
  left_join(indu, by="industry_code") %>%
  left_join(., area, by="area_fips") %>%
  select(-industry_code, -area_fips)
```

Variable names ([Descriptions](https://data.bls.gov/cew/doc/layouts/csv_annual_layout.htm))

```{r}
names(a1998.j)
```

Relevant variables:

38 - area_title
37 - industry_title
4 - year
8 - annual_avg_emplvl: "Annual average of monthly employment levels for a given year"
13 - avg_annual_pay: "Average annual pay based on employment and wage levels for a given year."
12 - annual_avg_wkly_wage: "Average weekly wage based on the 12-monthly employment levels and total annual wage levels."

Location quotients: "Location quotients are ratios that allow an area's distribution of employment by industry, ownership, and size class to be compared to a reference area's distribution."
16 - lq_annual_avg_emplvl
21 - lq_avg_annual_pay
20 - lq_annual_avg_wkly_wage


```{r}
colnames(a1998.j)[38] <- "Area"
colnames(a1998.j)[37] <- "Industry"
colnames(a1998.j)[4] <- "Year"
colnames(a1998.j)[8] <- "Annual Employment Level"
colnames(a1998.j)[16] <- "LQ Annual Employment"
colnames(a1998.j)[13] <- "Average Annual Pay"
colnames(a1998.j)[21] <- "LQ Annual Pay"
colnames(a1998.j)[12] <- "Annual Weekly Wages"
colnames(a1998.j)[20] <- "LQ Weekly Wages"

head(a1998.j)
```


# Narrowing

```{r}
a1998.w <- a1998.j %>%
  select(38, 37, 4, 8, 13, 12, 16, 21, 20) %>%

head(a1998.w)
```

```{r}
a1998.la_ca <- a1998.w %>%
  filter(a1998.w[1] == 'Los Angeles County, California')
```

```{r}
head(a1998.la_ca)
```



Test plot

- Axises = Employment level by Annual pay
- Points = Industry
- Facets =

```{r}
la_ca_plot1.indu_emplev <- a1998.la_ca %>%
  ggplot(aes(x = "Annual Employment Level", y = "Average Annual Pay")) +
  geom_point(col = a1998.la_ca$Industry["Service providing"])

la_ca_plot1.indu_emplev
```

